---
title: '"Project 1-Julien Sanseverino'
output: html_document
date: "2022-10-12"
---

```{r}
baseball_data<-read.csv("~/Documents/CPSC292/Project #1/foul-balls data.csv")
```

1.  Graph Represents the Distribution of Exit Velocities Hit into Each Zone

```{r}
library(ggplot2)
Zone<-factor(baseball_data$used_zone)
graph1<-ggplot(baseball_data, aes(x=Zone,y=exit_velocity, fill = Zone)) +
  geom_boxplot() + 
  scale_fill_manual(values=c("purple","blue","light green","maroon", "orange","pink","yellow")) +
  xlab("Zone") + ylab("Exit Velocity") + ggtitle("Exit Velocity vs Zone Baseball Landed")
print(graph1) +
theme_linedraw()

#fill=c("purple","blue","light green","maroon", "orange","pink","yellow")
```

Balls that reach zone 6 and 7 are some of the hardest hit balls, which makes sense since they are the zones in the outfield or furthest away. Zones 4 and 5 had the greatest range of exit velocities

2.  How accurately can we predict where foul balls are hit?


```{r}
baseball_data$correct<-baseball_data$used_zone==baseball_data$predicted_zone

newdf <- data.frame("Prediction" = c("Correct","Not Correct"), "value" =                c(sum(baseball_data$correct==TRUE)/length(baseball_data$correct),             sum(baseball_data$correct==FALSE)/length(baseball_data$correct)))

ggplot(newdf, aes(x="", y=value , fill = Prediction )) + 
ggtitle("Correct vs Incorrect Zone Prediction") +
theme(plot.title = element_text(hjust = 0.5), 
      axis.text = theme_void(TRUE),
      axis.ticks = theme_void(TRUE),
      panel.grid  = theme_void(TRUE)) +
geom_col(color="black") +
geom_text(aes(label=c("0.99", "0.01")), position=position_stack(vjust = 0.5)) +
coord_polar(theta="y") +
theme_void()

```

The pie chart represents the percentage of how accurately we were able to predict where a foul will land.

Correct= the predicted zone matched the "used zone" (actual zone where the ball landed). Incorrect= the predicted zone DID NOT match the "used zone" (actual zone where the ball landed).

99% of the foul balls hit landed in the predicted zones.

```{r}
correct<-baseball_data$predicted_zone==baseball_data$used_zone
as.numeric(correct)
table(correct)
11/906
895/906
```


Corrections:
Added a title for the legend and what the colors represent
Addded a main title for the pie chart so that we know what data we are looking at. 
ggtitle centering for title centering
got rid of grey background in pie chart
added a new title for legend in graph one
Shortened the graph title names